\begin{rubric}{\faBullhorn \textsc{Selected Outreach Activities}}
\entry*[]
\textbf{Video: ``Neutrino Masses: From Ghost Particles to Cosmological Tensions''} (2025 Annual Review of Nuclear and Particle Science Video Contest) \par
Co-produced with \textbf{Bernardita Ried Guachalla}. 
\href{https://www.youtube.com/watch?v=kna3FfmKTG8&t=18s}{Watch online}.

\entry*[]
\textbf{Radio Interview: ``El Ojo de la Mosca''}, Universal Sonica Radio. \par
Invited to present the DESI’s first-year cosmological results to a broad audience.

\entry*[]
\textbf{Speaker: ``Las Charlas de Cosmos''}, COSMOS Community. \par
Invited to give a talk on ``Explorando el Cosmos: La Estructura del Universo'' to a large Spanish-speaking audience. COSMOS has more than 2.4 million Facebook followers and over 2,000 YouTube subscribers. 
\href{https://www.youtube.com/watch?v=ui7ZfEto-Ws}{Watch recording}.

\entry*[]
\textbf{Active Member \& Treasurer}, SCOPE – Student Chapter of Optics and Photonics, University of the Atlantic, Colombia. \par
Led outreach activities promoting optics, photonics, astronomy, and cosmology. Affiliated with Optica Worldwide and SPIE. 
\href{https://henoriega.github.io/outreach/outreach4/}{More info}.

%\entry*[]
%\textbf{Featured Song for the DESI Collaboration}. \par
%Created a bilingual (English–Spanish) outreach song about the DESI experiment using AI-assisted tools to engage broader audiences.  
%\href{https://henoriega.github.io/outreach/}{Listen online (Outreach page)}  

\end{rubric}

