\begin{rubric}{\faCode \textsc{Code Development}}
\entry*[]
	\textbf{FOLPS}. Python package for computing galaxy Power Spectra and Bispectra in cosmologies with additional scales, such as massive neutrinos and selected modified gravity models. It is one of the main state-of-the-art codes worldwide for full-shape analysis, integrated into the official \texttt{cosmodesi} repository and actively used in DESI analyses. Available at: \url{https://github.com/henoriega/FOLPS-nu}.
    
\entry*[]
	  \textbf{\textsc{FOLPSax}}. JAX-based implementation of FOLPS, optimized for GPU acceleration and automatic differentiation. Enables fast, scalable, and differentiable full-shape modeling. Also integrated into the official \texttt{cosmodesi} repository and employed in DESI analyses. Available at: \url{https://github.com/cosmodesi/folpsax}.

\entry*[]
	  \textbf{\textsc{fkPT}}. Perturbation theory framework for $\Lambda$CDM and modified gravity models based on “fk”-kernels. Designed as a fast, brute-force approach that can incorporate scale-dependent effects, providing flexibility for testing beyond-$\Lambda$CDM physics. Currently employed within the DESI CPE and C3 working groups. Avaliable at: \url{https://github.com/henoriega/fkpt}.


\entry*[]
    \textbf{C2C}. Pipeline for mapping compressed parameters (from Standard and ShapeFit analyses) into cosmological parameter space. Provides an efficient interpretation layer between data compression techniques and cosmological inference. Employed in some DESI supporting papers: \href{https://arxiv.org/abs/2404.07269}{2404.07269} and \href{https://arxiv.org/abs/2404.07268}{2404.07268}. Avaliable at: \url{https://github.com/henoriega/C2C}.

\entry*[]
	  \textbf{Other codes}. Public packages for cosmology visualization, statistical analysis, and educational notebooks for learning and teaching cosmology concepts. Available at: \url{https://henoriega.github.io/codes/}.
\end{rubric}