\begin{rubric}{\faMicrophone \textsc{Charlas Seleccionadas}}
\entry*[]
        \textbf{Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), SLAC National Accelerator Laboratory, Estados Unidos.} \par
    \emph{“Are current neutrino mass constraints reliable? Insights from full-shape analyses.”} (Charla invitada)


\entry*[]
        \textbf{Kavli Institute for Particle Astrophysics, Stanford University, Estados Unidos.} \par
    \emph{“Large-scale structure formation in the presence of massive neutrinos.”} (Charla invitada)

\entry*[]
        \textbf{Leinweber Institute for Theoretical Physics, University of Michigan, Estados Unidos.} \par
    \emph{“Large-scale structure formation in the presence of massive neutrinos.”} (Charla invitada)

\entry*[]
    	\textbf{2025 Summer DESI Collaboration Meeting, Lawrence Berkeley National Laboratory, Estados Unidos.} \par
    \emph{“Cosmological Parameter Estimation (CPE) work within DESI.”} (Charla invitada como líder de neutrinos en DESI-CPE)

\entry*[]%
    	\textbf{Cosmology on the Beach: IX Essential Cosmology for the Next Generation, Playa del Carmen, México.} \par
    \emph{“Neutrino mass constraints: Insights from full-shape analyses.”}

\entry*[]
    	\textbf{DESI Year 1 Key Project Analysis Workshop, Ohio State University, Estados Unidos.} \par
    \emph{“RSD theoretical + fiducial cosmology: FOLPS \& fiducial covariance matrix.”}

\entry*[]%
    	\textbf{Institute of Space Science, Barcelona, España.} \par
    \emph{“Large-scale structure formation with scale-dependent linear growth function.”} (Charla invitada)

\entry*[]%
    	\textbf{DESI Conference, Durham University, Reino Unido.} \par
    \emph{“Exploring systematics in compressed and full-shape analyses of DESI Abacus mocks using FOLPS: Insights from Fourier space.”}


\entry*[]%
    	\textbf{Neutrinos from Home, Online.} \par
    \emph{“Large-scale structure formation in the presence of massive neutrinos.”}

\entry*[]%
	\textbf{V Joint ICTP-Trieste/ICTP-SAIFR School on Cosmology, IFT/Unesp, São Paulo, Brasil.}

\vspace{0.5cm}
    \textit{Charlas en español:}
\vspace*{0.5cm}

\entry*[]%
	\textbf{COSMOBASE Escuela de Verano, Universidad Veracruzana, Veracruz, México.} \par
\emph{“Lectures on Observational Cosmology.”} (Clases invitadas)

\entry*[]%
    \textbf{Panel de Discusión: Primeros Resultados Científicos del Sondeo DESI, Instituto de Astronomía, UNAM, Ciudad de México.} (Charla invitada \& Panel de discusión)

\entry*[]%
    \textbf{DESI-México: Una forma colaborativa de trabajo científico y sus resultados, Instituto de Ciencias Físicas, UNAM, Cuernavaca, México.} (Panel de discusión)

\entry*[]%
    \textbf{Mini-Curso: Métodos FFTLog en LCDM y teorías que contienen
escalas adicionales, Instituto Avanzado de Cosmología, México.} (Clases invitadas)

\end{rubric}
