\begin{rubric}{\faMicrophone \textsc{Selected Talks}}
\entry*[]
	\textbf{Kavli Institute for Particle Astrophysics and Cosmology (KIPAC), SLAC National Accelerator Laboratory, USA.} \par
    \emph{“Are current neutrino mass constraints reliable? Insights from full-shape analyses.”} (Invited Talk)


\entry*[]
	\textbf{Kavli Institute for Particle Astrophysics, Stanford University, USA.} \par
    \emph{“Large-scale structure formation in the presence of massive neutrinos.”} (Invited Talk)

\entry*[]
	\textbf{Leinweber Institute for Theoretical Physics, University of Michigan, USA.} \par
    \emph{“Large-scale structure formation in the presence of massive neutrinos.”} (Invited Talk)

\entry*[]
    \textbf{2025 Summer DESI Collaboration Meeting, Lawrence Berkeley National Laboratory, USA.} \par
    \emph{“Cosmological Parameter Estimation (CPE) work within DESI.”} (Invited Talk as DESI-CPE neutrino lead)

\entry*[]%
    \textbf{Cosmology on the Beach: IX Essential Cosmology for the Next Generation, Playa del Carmen, Mexico.} \par
    \emph{“Neutrino mass constraints: Insights from full-shape analyses.”}

\entry*[]
    \textbf{DESI Year 1 Key Project Analysis Workshop, Ohio State University, USA.} \par
    \emph{“RSD theoretical + fiducial cosmology: FOLPS \& fiducial covariance matrix.”}

\entry*[]%
    \textbf{Institute of Space Science, Barcelona, Spain.} \par
    \emph{“Large-scale structure formation with scale-dependent linear growth function.”} (Invited Talk)

\entry*[]%
    \textbf{DESI Conference, Durham University, UK.} \par
    \emph{“Exploring systematics in compressed and full-shape analyses of DESI Abacus mocks using FOLPS: Insights from Fourier space.”}


\entry*[]%
    \textbf{Neutrinos from Home, Online.} \par
    \emph{“Large-scale structure formation in the presence of massive neutrinos.”}

\entry*[]%
\textbf{V Joint ICTP-Trieste/ICTP-SAIFR School on Cosmology, IFT/Unesp, São Paulo, Brazil.}

\vspace{0.5cm}
\textit{Spanish Talks:}
\vspace*{0.5cm}

\entry*[]%
\textbf{COSMOBASE Summer School, Universidad Veracruzana, Veracruz, Mexico.} \par
\emph{“Lectures on Observational Cosmology.”} (Invited Lectures)

\entry*[]%
\textbf{Discussion Panel: First Scientific Results from the DESI Survey, Instituto de Astronomía, UNAM, Mexico City.} (Invited Talk \& Panel Discussion)

\entry*[]%
\textbf{DESI-Mexico: Collaborative Scientific Work and Results, Instituto de Ciencias Físicas, UNAM, Cuernavaca, Mexico.} (Panel Discussion)

\entry*[]%
\textbf{Mini-Course: FFTLog Methods in $\Lambda$CDM and Theories with Additional Scales, Instituto Avanzado de Cosmología, Mexico.} (Invited Lectures)



\end{rubric}


